I Compensate, therefore I Am \\ (accurate for DNN verification)

### 2024-01-26 Paper/proofs.tex
th3

			$$\max(b)=\max_{\vx_j} \val_{\vx^{\star}_I,\vx_J}(b)$$
			$$\min(b)=\max_{\vx_j} \val_{\vx^{\sharp}_I,\vx_J}(b)$$
			and for $S(b)=-1$:

			$$\max(b)=\max_{\vx_j} \val_{\vx^{\sharp}_I,\vx_J}(b)$$
			$$\min(b)=\max_{\vx_j} \val_{\vx^{\star}_I,\vx_J}(b)$$
			\end{corollary}

@@

			We denote by $X=B_{open}$, and consider $\MILP_{X}$.
			Let $[\alpha,\beta]$ be the bounds computed by $\MILP_{X}$ for the target node $z$. We want to show that $\beta= \max(z)$. 
			%As the MILP abstraction is a sound over-approximation, it suffices to show that %$\beta\leq \max (z)$.
			The case for $\alpha$ is similar.

@@

We are now ready to finish the proof of Theorem \ref{thm:2}.

@@

			Now, we show that Theorem \ref{thm:2} can prove Theorem \ref{th2}. Suppose $a$ is a node in a weak compensating path $P$, and $P,P'$ form this weak compensating pair.

			Cut $P,P'$ into segments $P_0,P_1,\cdots$, and $P'_0,P'_1,\cdots$ at each common node; hence each $P_i,P_i'$ either have not common nodes (except the start and end nodes), or are the same. Now, for node $a$, there are three cases:
			\begin{itemize}
				\item $a$ is a common nodes.

				\item  $a$ is a in path $P_i$ such that weights of $P_i,P_i'$ have the same sign.

				\item  $a$ is a in path $P_i$ such that weights of $P_i,P_i'$ have the different sign.
			\end{itemize}

>>>>

			$$\max(b)=\max_{\vx_J} \val_{\vx^{\star}_I,\vx_J}(b)$$
			$$\min(b)=\max_{\vx_J} \val_{\vx^{\sharp}_I,\vx_J}(b)$$
			and for $S(b)=-1$:

			$$\max(b)=\max_{\vx_J} \val_{\vx^{\sharp}_I,\vx_J}(b)$$
			$$\min(b)=\max_{\vx_J} \val_{\vx^{\star}_I,\vx_J}(b)$$
			\end{corollary}

@@

			%We want to show that $\beta= \max(z)$. 
			%As the MILP abstraction is a sound over-approximation, it suffices to show that %$\beta\leq \max (z)$.
			%The case for $\alpha$ is similar.

@@

	We denote by $X=B_{open}$, and consider $\MILP_{X}$.
	Let $[\alpha,\beta]$ be the bounds computed by $\MILP_{X}$ for the target node $z$. We are now ready to finish the proof of Theorem \ref{thm:2}.

@@

			We now show Theorem \ref{th2} from Theorem \ref{thm:2}.
			Assume that $n$ is a node in a weakly compensating path $\rho$.

			There are three mutually exclusive cases:
			\begin{enumerate}
				\item $n$ is on a compensating pair of paths $\rho,\rho'$ to $z$ (but not its source or target), otherwise:

				\item $n$ is on a compensating pair of paths $\rho,\rho'$ to $z' \neq z$ (but not its source or target), otherwise:

				\item $n$ is not on any compensating pair of paths to any node (except may be as source or target).
			\end{enumerate}

			In the first case, the ReLU for $n$ will be opened, so we do not need to worry about this case.

			In the other cases, the ReLU associated with node $n$ will not be in $X$ 
			(not opened in $\MILP_X$).
			In the second case, as we assumed without loss of generality that $z$ was the unique output node, it means that $z'$ is in a layer strictly before $z'$.
			Consider all the possible associated $z'$.
